The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-11 analysis/paper/paper.qmd
Add anonymisation stop words

meta_sw <- find_meta_stopwords(emu)
urbanism_sw <- urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism", 
                      "european post master in urbanism",
                      "european postmaster in urbanism",
                      "tu delft", "ku leuven", "upc barcelona", "iuav venice"))
thesis_sw <- thesis_stopwords(add_stopwords = c("advisor", "prof", "fig", "ure", "ning"))
custom_sw <- c("space", "spatial", "spaces", "plan", "public", "development") |>
  (\(.) paste0("\\b", ., "\\b"))() |> 
  paste(collapse = "|")

# Add cleaned text column
emu$text_clean <- emu$text_raw |>
  # Remove white spaces and punctuation, and change text to lower-case
  clean_basic() |>
  # Remove title, subtitle and full title
  str_remove_all(meta_sw) |> 
  # Remove dataset-specific words
  str_remove_all(urbanism_sw) |>
  # Remove thesis-specific words
  str_remove_all(thesis_sw)

>>>>

meta_sw <- find_meta_stopwords(emu)
urbanism_sw <- urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism", 
                      "european post master in urbanism",
                      "european postmaster in urbanism",
                      "tu delft", "ku leuven", "upc barcelona", "iuav venice"))
thesis_sw <- thesis_stopwords(add_stopwords = c("advisor", "prof", "fig", "ure", "ning"))
ananymisiation_sw <- c("EMAIL_REMOVED", "AUTHOR_REMOVED", "FIRST_NAME_REMOVED", "LAST_NAME_REMOVED") |>
  paste(collapse = "|")
custom_sw <- c("space", "spatial", "spaces", "plan", "public", "development") |>
  (\(.) paste0("\\b", ., "\\b"))() |> 
  paste(collapse = "|")

# Add cleaned text column
emu$text_clean <- emu$text_raw |>
  # Remove white spaces and punctuation, and change text to lower-case
  clean_basic() |>
  # Remove title, subtitle and full title
  str_remove_all(meta_sw) |> 
  # Remove dataset-specific words
  str_remove_all(urbanism_sw) |>
  # Remove thesis-specific words
  str_remove_all(thesis_sw) |> 
  # Remove text included with anonymisation
  str_remove_all(ananymisiation_sw)
